Title: Discrete and Continuous Probability Distributions
========================================================

Packages: gridExtra, knitr
Discrete Variable: I am sending this report to my senior manager who asked me
to analyses how much our customers visiting the desired links on our website -
which is called conversion rate - and how can we improve the profit.
I have with me the rate of conversion and their respective probability of occurring,
also, how much profit we get from that conversion rate.
In this way I can determine what audience to target to give more improved website
experience so that more profit can be generated from them.

```{r}
library(gridExtra)
Conversion_rate <- 1:10
probability <- c(.2,.1,.15,.24,.09,.07,.06,.06,0.02,.01)
profit <- c(23,65,76,77,84,90,98,100,105,200)

expected_value <- (probability * profit)


d <- data.frame(Conversion_rate,probability,profit,expected_value)
grid.table(d)
print(paste("mean is",mean(d$expected_value)))
print(paste("variance is",var(d$expected_value)))
print(paste("standard dev is",sd(d$expected_value)))
print(paste("lower limit is", mean(d$expected_value) - sd(d$expected_value)))
print(paste("upper limit is", mean(d$expected_value) + sd(d$expected_value)))
```

Observation: If we compare the upper value and lower value with the conversion
rate we have, and since it was discrete value, we can see that conversion rate 3 to
10 lies in that category. By that we can determine that the 70% of conversion rate
that amounts to some profit to our website (1 to 3), rest 30% does not amount
much, and hence, we should not worry about users who have a conversion rate of 1
or 2 or 3.


Continuous Variable: In the dataframe, we have time as a continuous variable.
The probability that a flight will take off between that 1 hour timeframe at each
interval is also given. Then a column represent the number of passengers that
usually come to airport to have taken a flight. By doing this probability distribution
we can determine as to at what time do we have the highest risk of losing a
customer because he misses his flight.

```{r}
time_PM <- seq(12,24,by=1)
probabilities <- c(0.000, 0.001, 0.008, 0.036 ,0.109, 0.213 ,0.266, 0.213
,0.109, 0.036, 0.008, 0.001,0.00)
Number_of_passengers <- c(00,80,70,69,56,45,30,42,49,53,67,78,00)
expected_value <- probabilities * Number_of_passengers
tab <- grid.table
join <- data.frame(time_PM,probabilities,Number_of_passengers,expected_value)
join <- join[-1,]
join <- join[-12,]
tab <- grid.table(join)
print(paste("total expected value",sum(join$expected_value)))
plot(join$time_PM,join$probabilities,type="l",xlab="Time in
PM",ylab="probability")
abline(v=17, col="red", lty=3)
prob <- sum(join$probabilities[which(time_PM< 17)])
print(paste("probability that a flight will take off before 5PM or 17hr is:",
round(prob,3)))
print(paste("mean is",mean(join$expected_value)))
print(paste("standard deviation is:",sd(join$expected_value)))
```

Observation: In this we can see that the probability that a plane will take off
before 5PM is 0.367.


